A dataset of Scratch programs,\\Scraped, Shaped and Scored

### 2017-02-09 MSR-Scratch.tex
DB Schema table

>>>>

\begin{table}[ht]
	\centering
	\begin{tabular}{llp{5.4cm}}
		\textbf{Table}& \textbf{Key} & \textbf{Attribute(Description)}\\
		\hline
		\textbf{\texttt{project}} & PK & \texttt{p\_id} (Scratch project ID)\\
		&  & 							\texttt{project-name} (name given to project)\\
		&  & 							\texttt{username} (author's Scratch 
		username)\\
		&  & 							\texttt{total-views} (project views number)\\
		&  & 							\texttt{total-remixes} (project remixes number)\\
		&  & 							\texttt{total-favorites} (total users favoriting)\\
		&  & 							\texttt{total-loves} (total users `loving' the project)\\
		& & 							\texttt{is-remix} (calculated column, true if project is a remix of another one)\\
		\hline
		\textbf{\texttt{script}} & PK & \texttt{script\_id} (auto increment)\\
		& FK & 							\texttt{project\_id} (\scriptsize{\texttt{*\ldots1 project:p\_id}})\\
		& & 							\texttt{sprite-type} (one of [sprite, stage, procDef])\\
		& & 							\texttt{sprite-name} (name sprite the script is in)\\
		& & 							\texttt{script-rank} (project-level ranking of script)\\
		& & 							\texttt{coordinates} (x-y location of script in Scratch editor)\\
		& & 							\texttt{total-blocks} (calculated column, number of blocks comprising the script)\\
		\hline
		\textbf{\texttt{procedure}} & PK,FK & \texttt{script\_id} (\scriptsize{\texttt{1\ldots1 script:script\_id}})\\
		& & 							\texttt{proc-name} (name given to custom block)\\
		& & 							\texttt{total-args} (number of input arguments)\\
		\hline
		\textbf{\texttt{block}} & PK,FK  & \texttt{script\_id} (\scriptsize{\texttt{*\ldots1 script:script\_id}})\\
		& PK & \texttt{block-rank} (script-level ranking of block)\\
		& FK & \texttt{block-type} (\scriptsize{\texttt{*\ldots1 blockType:b-type}})\\
		&  & \texttt{parameter-1} (value of 1st input parameter)\\
		&  &\vdots\\
		&  & \texttt{parameter-24} (value of 24th input parameter)\\
		\hline
		\textbf{\texttt{blockType}} & PK & \texttt{b-type} (Scratch name of predefined block)\\
		&  & \texttt{category} (Scratch block category)\\
		&  & \texttt{shape} (One of the 8 block shapes in the Scratch interface)\\
		&  & \texttt{is-input} (true if the block receives user input)\\
		\hline
		\textbf{\texttt{remix}} & PK  & \texttt{remix\_id} (\texttt{\scriptsize{project\_id}} of created project)\\
		&  & \texttt{from-project\_id} (\texttt{\scriptsize{project\_id}} of original project)\\
		\hline
		\textbf{\texttt{grades}} & PK,FK & \texttt{project\_id} (\texttt{\scriptsize{1\ldots1 project:p\_id}})\\
		& & \texttt{Abstraction} ()\\
		& & \texttt{Parallelism} ()\\
		& & \texttt{Logic} ()\\
		& & \texttt{Synchronization} ()\\
		& & \texttt{FlowControl} ()\\
		& & \texttt{UserInteractivity} ()\\
		& & \texttt{DataRepresentation} ()\\
		& & \texttt{Mastery} ()\\
		& & \texttt{Clones} ()\\
		& & \texttt{CustomBlocks} ()\\
		& & \texttt{InstancesSprites} ()\\
		\hline
	\end{tabular}
	\caption{Database schema: Tables and Attributes}
	\label{tbl-dbschema}
\end{table}
